% Shubham Tiwari — resume
% Compile: docker run --rm -v "$PWD":/work -w /work texlive/texlive:latest-small pdflatex resume.tex
% Output goes to public/resume.pdf via: cp resume.pdf ../public/resume.pdf
\documentclass[letterpaper,10pt]{article}

\usepackage[margin=0.5in,top=0.42in,bottom=0.42in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\leftmargini}{1.15em}

% --- helpers -----------------------------------------------------------
\newcommand{\sectionrule}[1]{%
  \vspace{5pt}%
  {\large\scshape\bfseries #1}\par\vspace{1pt}\hrule\vspace{3pt}%
}
\newcommand{\entry}[2]{%
  \textbf{#1} \hfill {\small #2}\par%
}
\newcommand{\subentry}[2]{%
  {\itshape #1} \hfill {\small\itshape #2}\par\vspace{1pt}%
}
\newenvironment{bullets}{%
  \begin{itemize}\setlength{\itemsep}{1pt}\setlength{\parskip}{0pt}
\setlength{\leftmargini}{1.15em}\setlength{\topsep}{2pt}%
}{\end{itemize}\vspace{2pt}}

\begin{document}

% --- header ------------------------------------------------------------
\begin{center}
  {\LARGE\bfseries SHUBHAM TIWARI}\\[3pt]
  {\small 9323315388 \;\textperiodcentered\; \href{mailto:shubht3303@gmail.com}{shubht3303@gmail.com}
  \;\textperiodcentered\; \href{https://github.com/0xshubhs}{github.com/0xshubhs}
  \;\textperiodcentered\; \href{https://www.0xshubhs.com}{0xshubhs.com}
  \;\textperiodcentered\; \href{https://x.com/shubhamtwtt}{x.com/shubhamtwtt}}
\end{center}

% --- summary -----------------------------------------------------------
\sectionrule{Summary}
Blockchain engineer working across EVM infrastructure, privacy tech (FHE, ZK), and custom chain deployments.
Lead engineer on a production RWA exchange running its own chain; built PoA networks on Reth, shipped Solidity
governance and audit-trail systems, and won six paid hackathons across FHE, ZK, and payments tracks.

% --- education ---------------------------------------------------------
\sectionrule{Education}
\entry{Lokmanya Tilak College of Engineering}{Mumbai, India}
\subentry{Bachelor of Engineering in Computer Engineering -- 8.6 GPA}{May 2025}

% --- tech & oss --------------------------------------------------------
\sectionrule{Technologies \& Open Source}
\begin{bullets}
  \item \textbf{Blockchain \& EVM:} Solidity, Foundry, Hardhat, Viem, Wagmi, Ethers.js, Avalanche Subnets, Reth, EVM internals
  \item \textbf{Privacy:} FHE (Zama FHEVM, Fhenix CoFHE, Inco Lightning), ZK (Aleo/Leo), sealed-bid auctions, confidential payments
  \item \textbf{Languages \& Infra:} Rust, Go, TypeScript, Node.js, Next.js, AWS, Docker, Kubernetes, Cloudflare Workers
  \item \textbf{Open Source:} 143 merged PRs -- DefiLlama TVL adapter fix, Foundry book (\texttt{vm.parseJsonKeys} docs),
        Starknet Quest Rust API perf optimization, Witnet \texttt{elliptic-curve-solidity}
\end{bullets}

% --- experience --------------------------------------------------------
\sectionrule{Experience}

\entry{Qoneqt (Human Quotient Pvt Ltd)}{Remote}
\subentry{Blockchain Engineer}{April 2025 -- Present}
\begin{bullets}
  \item Lead engineer on \textbf{Maha Fraxn}, the company's RWA exchange: 700+ commits ($\sim$89\% of the codebase) across
        Solidity contracts, a dedicated EVM chain with block explorer, and the Go/TypeScript backend.
  \item Designed the on-chain audit trail (bytes32 listing IDs, trade metadata) and admin platform: trade monitoring
        with exports, fee statistics, side-aware market-maker fees, and KYC flows.
  \item Shipped i18n covering all 22 Indian scheduled languages and hardened the stack with fixes from parallel security audits.
  \item Deployed custom L1s on Avalanche Subnets with tailored precompiles (gas, rewards, fees) -- cut block time 40\%
        over default config.
  \item Built Subgraph + fallback Node.js indexer for the Oboswap DEX (query latency $\sim$2s $\rightarrow$ under 200ms) and
        gasless transactions (EIP-712/EIP-2771) that removed 60\%+ onboarding drop-off.
\end{bullets}

\entry{Attenomics Labs}{Remote}
\subentry{Solidity Engineer}{Feb 2025 -- Present}
\begin{bullets}
  \item Wrote end-to-end test suites across the full contract surface: reentrancy, access control, overflows, storage collisions.
  \item Built internal tooling to flag front-running, MEV sandwich vectors, and price manipulation in pending tx flows.
  \item Audited proxy/UUPS upgrade patterns for storage layout conflicts and initialization bugs.
\end{bullets}

% --- projects ----------------------------------------------------------
\sectionrule{Projects \& Hackathon Wins}

\entry{Sigill -- \href{https://www.sigill.store/}{sigill.store}}{Fhenix CoFHE Builder Waves -- 850 USDT won}
\begin{bullets}
  \item Private FHE checkout on Base Sepolia: encrypted product IDs and amounts, confidential cUSDC escrow, bonded
        observers fulfilling gift-card orders, AES-wrapped codes only the buyer can unseal.
\end{bullets}

\entry{SilentBid -- \href{https://github.com/0xshubhs/aleo-}{Github}}{Aleo Privacy Buildathon Winner -- 178 USDT}
\begin{bullets}
  \item Sealed-bid ZK auctions live on Aleo testnet: commit-reveal with BHP256 commitments and uniform max-bid escrow
        so bids leak zero information; Chainlink CRE variant for Uniswap CCA token launches.
\end{bullets}

\entry{x402 Sessions -- \href{https://www.npmjs.com/package/elsa-x402-sessions}{npm}}{x402 Buildathon -- 200 USDC won}
\begin{bullets}
  \item Sign-once settle-many x402 micropayments: TypeScript SDK on npm, hosted facilitator, and a confidential Solana
        variant with encrypted amounts on Inco Lightning.
\end{bullets}

\entry{Custom-reth-chain -- \href{https://github.com/0xshubhs/custom-reth-chain}{Github}}{Rust, Solidity, Docker}
\begin{bullets}
  \item Full PoA blockchain on Reth, EVM-compatible through Prague: consensus validation, signer-key block production,
        on-chain governance for chain config and treasury; 194 passing tests.
\end{bullets}

\textbf{Other wins:} {\small FomoWallet (EthIndia 2024, 350 USDC + Graph Top 10 + Excellence in Privacy), AutoFund AI \&
MarketMind (SoSoValue Buildathon, 100+ USDT each), StealthPass (UNFOLD 2024 Avalanche track winner).}

\end{document}
